Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-16 demystify.tex
updates

\paragraph{Intellectual merit (IM)} IM evaluates your research potential, e.g., your research experience, your potential to do research, and how you can contribute to the field.   Unlike a normal project or research proposal, in which the evaluation is entirely based on the project, in the GRFP, the evaluation is \emph{not} entirely about the research plan. We are repeatedly reminded to not focus too much on the research plan as many applicants are still applying for PhD programs and might not even get into the field or work with a prof. that fit their research plan.

@@

The NDSEG is another prestigious fellowship supporting \emph{U.S. citizens} pursuing advanced degrees in STEM fields \emph{critical to national defense} (such as CS). NDSEG has several differences from NSF GRFP, e.g., it redacts more information from the reviewers and focuses more on defense-related research.

>>>>

\paragraph{Intellectual merit (IM)} IM evaluates your research potential, e.g., your research experience, your potential to do research, and how you can contribute to the field.   Unlike a normal project or research proposal, in which the evaluation is entirely based on the merits of the proposed work, in the GRFP, the evaluation is \emph{not} entirely about the research plan. Reviewers are repeatedly reminded to not focus too much on the research plan as many applicants are still applying for PhD programs and might not even get into the field or work with a prof. that fit their research plan.

@@

The NDSEG is another prestigious fellowship supporting \emph{U.S. citizens} pursuing advanced degrees in STEM fields \emph{critical to national defense} (such as CS). NDSEG has several differences from NSF GRFP, e.g., it redacts more information from the reviewers and focuses more on application to DoD.
